14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-18 rules/rules19.tex
describe website and tools

\header{Competition Website}

\todo{Giles: Add text about the fact that we will use the competition website to include links to tools, announce results etc... including archiving}
%

\header{Tools} \todo{link to scrambler, trace executor, benchmark selection script, postprocessors}

@@

\header{Benchmark selection.}
%
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In all tracks the following
process will be used for culling the benchmark pool.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The competition
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy benchmarks.} The competition organizers will
  remove all benchmarks that were solved by all solvers (including the
  non-competitive solvers) in the 2018 SMT competition.
\item \emph{Cap the number of instances in a division.} The competition
  organizers will limit the number of benchmarks in a division as
  follows:
  \begin{enumerate}
  \item If a division contains less than 300 instances, all
        the instances will selected.
  \item If a division contains between 300 and 600 instances,
        a selection of 300 instances from the set will be selected.
  \item If a division contains more than 600 instances, 50\% of
        the benchmarks will be selected.
  \end{enumerate}
\item \emph{\ucoretrack{}.} In addition, for the \ucoretrack{}, all
  benchmarks with a single assertion will be removed.
\end{enumerate}
%
The selection process in cases (b) and (c) above will guarantee the
inclusion of new benchmarks by first picking randomly one benchmark from
each new benchmark family.  The rest of the benchmarks will be chosen
randomly from the remaining benchmarks using a uniform distribution.
%
The culling script will be publicly available and will use the same
random seed as the rest of the competition.  The set of benchmarks
selected for the competition will be published when the competition
begins.

>>>>

\header{Competition Website.} 
The competition website (\url{www.smtcomp.org}) will be used as the main form of communication for the competition. The website will be used to post updates, link to these rules and other relevant information (e.g. the benchmarks), and to announce the results. We also use the website to archive previous competitions. Starting from 2019 we will include the submitted solvers in this archive to allow reproduction of the competition results in the future.
%

\header{Tools.} 
The competition uses a number of its own tools/scripts to run the competition. We briefly describe these tools. Unless stated otherwise the tools are found at \url{https://github.com/SMT-COMP/smt-comp/tree/master/tools}. {\color{red} Some tools have not been released yet.}
\begin{itemize}
	\item \textbf{Benchmark Selection.} This script implements the benchmark selection policy described on page~\pageref{benchmark-selection}. It takes a seed for the random benchmark selection. The same seed is used for all tools requiring randomisation.
	\item \textbf{Scramber.} This tool is used to scramble benchmarks during the competition to ensure that tools do not rely on syntactic features to identify benchmarks. The scramber can be found at \url{https://github.com/SMT-COMP/scrambler}.
	\item \textbf{Trace Executor.} This tool is used in the interactive track to emulate an on-line interaction between an SMT solver and a client application and is available at \url{https://github.com/SMT-COMP/trace-executor}
	\item \textbf{Postprocessors.} These are used by StarExec to translate the output of tools to the format required for scoring. The postprocessors (per track) are available at \url{https://github.com/SMT-COMP/postprocessors}.
	\item \textbf{Scoring.} This script implements the scoring computation described on in Section~\ref{sec:scoring}. It also includes the scoring computations used in previous competitions (since 2015).
\end{itemize}

@@

\header{Benchmark selection.} \label{benchmark-selection}
%
The competition will use a large subset of SMT-LIB benchmarks, with some
guarantees on including new benchmarks.  In all tracks the following
process will be used for culling the benchmark pool.
\begin{enumerate}
\item \emph{Remove inappropriate benchmarks.} The competition
  organizers may remove benchmarks that are deemed inappropriate or
  uninteresting for competition, or cut the size of certain benchmark
  families to avoid their over-representation.  SMT-COMP attempts to
  give preference to benchmarks that are ``real-world,'' in the sense
  of coming from or having some intended application outside SMT.
\item \emph{Remove easy benchmarks.} The competition organizers will
  remove all benchmarks that were solved by all solvers (including the
  non-competitive solvers) in the 2018 SMT competition.
\item \emph{Cap the number of instances in a division.} The competition
  organizers will limit the number of benchmarks in a division as
  follows:
  \begin{enumerate}
  \item If a division contains less than 300 instances, all
        the instances will selected.
  \item If a division contains between 300 and 600 instances,
        a selection of 300 instances from the set will be selected.
  \item If a division contains more than 600 instances, 50\% of
        the benchmarks will be selected.
  \end{enumerate}
\item \emph{\ucoretrack{}.} In addition, for the \ucoretrack{}, all
  benchmarks with a single assertion will be removed.
\end{enumerate}
%
The selection process in cases (b) and (c) above will guarantee the
inclusion of new benchmarks by first picking randomly one benchmark from
each new benchmark family.  The rest of the benchmarks will be chosen
randomly from the remaining benchmarks using a uniform distribution.
%
The culling script will be publicly available and will use the same
random seed as the rest of the competition.  The set of benchmarks
selected for the competition will be published when the competition
begins.
